### 2023-10-03 appendices/paper_brief.tex
Work on abstract and discussion

\begin{figure}[!t]
    \begin{flushleft}
        \textsc{\small \hspace{0.16\textwidth} self-supervised \hspace{0.22\textwidth} latent variable}
    \end{flushleft}
    \centering
    \includegraphics[width=0.90\textwidth]{paper_brief/SSL_LVM.pdf}
    \caption{A schematic overview of the two groups of models covered in this survey. \textit{Left}: A model trained with self-supervised learning. We take these models to consist of two functions $f(\cdot)$ and $g(\cdot)$ (\cref{ssec:notation}). After pre-training, $f(\cdot)$ is fine-tuned or used for extracting features $\mathbf{c}$. $g(\cdot)$ is an auxiliary function used to accommodate the self-supervised pre-training task. \textit{Right}: A probabilistic latent variable model. In contrast to the self-supervised model, the functions $f(\cdot)$ and $g(\cdot)$ learn the parameters of distributions $q$ and $p$. The latent variable $\mathbf{z}$ is commonly used for representation learning.}
    \label{fig:ssl_lvm}
\end{figure}

@@

\begin{sidewaystable*}[t]
    \caption{Selected models classified according to the binary attributes identified throughout the text. The models are sorted according to first publication date on arXiv which might differ from the citation year. \textbf{\textsc{msk}}: masking, \textbf{\textsc{prd}}: prediction, \textbf{\textsc{con}}: contrastive, \textbf{\textsc{rec}}: reconstruction, \textbf{\textsc{qtz}}: quantization, \textbf{\textsc{gen}}: generative, \textbf{\textsc{frz}}: frozen, \textbf{\textsc{ftn}}: fine-tuned, \textbf{\textsc{loc}}: local, \textbf{\textsc{glo}}: global.}
    \label{tab:model-taxonomy}
    \begin{center}
        \renewcommand{\arraystretch}{1.1}
        \resizebox{0.925\textwidth}{!}{%
        \begin{tabular}{ l l | c c c c c c | c c c | c c } 
            \toprule

@@

\begin{table}[t!]
\caption{A comprehensive overview of observation, prior and inference models for VAE type latent variable models with a single latent variable. The observation, prior and inference models may all belong to one or more of the categories listed under them as detailed in \cref{sec:plvms}. The types listed here serve as primitives from which more complex structures can be constructed including models with hierarchies of multiple latent variables.}
\label{tab:lvm-model-primitives}
\begin{center}
    % \renewcommand{\arraystretch}{1.1}
    % \resizebox{0.8\columnwidth}{!}{%
    \begin{tabular}{ l l l } 
        \toprule
        \multicolumn{2}{l}{\textbf{\textsc{Type}}} & \textbf{\textsc{Form}} \\
        \midrule
        \multicolumn{3}{c}{\textsc{Observation model}} \\
        \midrule
        \textbf{\textsc{arx}} & Autoregressive on $\mathbf{x}_t$      & $p(\mathbf{x}_t|\mathbf{x}_{1:t-1})$ \\
        \textbf{\textsc{loc}} & Local latent variable                 & $p(\mathbf{x}_{t}|\mathbf{z}_{1:t})$ \\
        \textbf{\textsc{glb}} & Global latent variable                & $p(\mathbf{x}_{t}|\mathbf{z})$ \\
        \midrule
        \multicolumn{3}{c}{\textsc{Prior}} \\
        \midrule
        \textbf{\textsc{arx}} & Autoregressive on $\mathbf{x}_t$      & $p(\mathbf{z}_t|\mathbf{x}_{1:t-1})$ \\
        \textbf{\textsc{arz}} & Autoregressive on $\mathbf{z}_t$      & $p(\mathbf{z}_t|\mathbf{z}_{1:t-1})$ \\
        \textbf{\textsc{ind}} & Locally independent $\mathbf{z}_t$                 & $p(\mathbf{z}_t)$ \\
        \textbf{\textsc{glb}} & Global latent variable                & $p(\mathbf{z})$ \\
        \midrule
        \multicolumn{3}{c}{\textsc{Inference model}} \\
        \midrule
        \textbf{\textsc{arz}} & Autoregressive on $\mathbf{z}_t$      & $q(\mathbf{z}_t|\mathbf{z}_{1:t-1})$ \\
        \textbf{\textsc{flt}} & Filtering                             & $q(\mathbf{z}_t|\mathbf{x}_{1:t})$ \\
        \textbf{\textsc{lsm}} & Local smoothing                       & $q(\mathbf{z}_t|\mathbf{x}_{t-r:t+r})$ \\
        \textbf{\textsc{gsm}} & Global smoothing                      & $q(\mathbf{z}_t|\mathbf{x}_{1:T})$ \\
        \textbf{\textsc{glb}} & Global latent variable                & $q(\mathbf{z}|\mathbf{x}_{1:T})$ \\
        \bottomrule
    \end{tabular}
    % }
    \end{center}
\end{table}

\begin{sidewaystable*}[t]
    \caption{Selected latent variable models classified according the attributes defined throughout \cref{sec:plvms}. See \cref{tab:lvm-model-primitives} for the probability distributions that correspond to each of the attribute short-hands. \textbf{\textsc{hie}} indicates a hierarchical representation.}
    \label{tab:lvm-taxonomy}
    \begin{center}
        \renewcommand{\arraystretch}{1.1}
        \resizebox{0.99\textwidth}{!}{% <------ Don't forget this %
        \begin{tabular}{ l l | c c c | c c c c | c c c c c | c } 
            \toprule
            \multicolumn{2}{c}{} & 
            \multicolumn{3}{c}{\footnotesize\textsc{Observation}} & 
            \multicolumn{4}{c}{\footnotesize\textsc{Prior}} & 
            \multicolumn{5}{c}{\footnotesize\textsc{Inference}} \\
            \textbf{\textsc{model}} & 
            \textbf{\textsc{pub. date}} &
            \textbf{\textsc{arx}} & 
            \textbf{\textsc{loc}} & 
            \textbf{\textsc{glb}} &  
            \textbf{\textsc{arx}} & 
            \textbf{\textsc{arz}} & 
            \textbf{\textsc{ind}} & 
            \textbf{\textsc{glb}} &  
            \textbf{\textsc{arz}} & 
            \textbf{\textsc{flt}} & 
            \textbf{\textsc{lsm}} & 
            \textbf{\textsc{gsm}} & 
            \textbf{\textsc{glb}} &
            \textbf{\textsc{hie}} \\
            \midrule
            %                                                              OBSERVATION       |              PRIOR                |                  INFERENCE       
            %                                                         ARX      LOC      GLB      ARX      ARZ     IND      GLB      ARZ      FLT      LSM      GSM      GLB
            \textbf{VRNN} \footnotesize\parencite{chung_recurrent_2015}          & 2015 Jun. & \cmark & \cmark & \xmark & \cmark & \cmark & \xmark & \xmark & \cmark & \cmark & \xmark & \xmark & \xmark & \xmark \\
            \textbf{SRNN} \footnotesize\parencite{fraccaro_sequential_2016}      & 2016 May  & \cmark & \cmark & \xmark & \cmark & \cmark & \xmark & \xmark & \cmark & \xmark & \xmark & \cmark & \xmark & \xmark \\
            \textbf{HMM-VAE} \footnotesize\parencite{ebbers_hidden_2017}         & 2017 Mar. & \xmark & \cmark & \xmark & \xmark & \cmark & \xmark & \xmark & \cmark & \cmark & \xmark & \xmark & \xmark & \cmark \\
            \textbf{ConvVAE} \footnotesize\parencite{hsu_learning_2017}          & 2017 Apr. & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark & \cmark & \cmark & \xmark \\
            \textbf{FHVAE} \footnotesize\parencite{hsu_unsupervised_2017}        & 2017 Sep. & \xmark & \cmark & \cmark & \xmark & \xmark & \cmark & \cmark & \xmark & \xmark & \xmark & \cmark & \cmark & \cmark \\
            \textbf{VQ-VAE} (van den Oord et al. 2018)            & 2017 Nov. & \cmark & \cmark & \xmark & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark \\
            \textbf{BHMM-VAE} \footnotesize\parencite{glarner_full_2018}         & 2018 Mar. & \xmark & \cmark & \xmark & \xmark & \cmark & \xmark & \xmark & \cmark & \cmark & \xmark & \xmark & \xmark & \xmark \\
            \textbf{STCN} \footnotesize\parencite{aksan_stcn_2019}               & 2019 Feb. & \xmark & \cmark & \xmark & \cmark & \xmark & \xmark & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark & \cmark \\
            \textbf{FDMM} \footnotesize\parencite{khurana_factorial_2019}        & 2019 Oct. & \xmark & \cmark & \cmark & \xmark & \cmark & \xmark & \cmark & \cmark & \cmark & \xmark & \xmark & \cmark & \cmark \\
            \textbf{ConvDMM} \footnotesize\parencite{khurana_convolutional_2020} & 2020 Jun. & \xmark & \cmark & \xmark & \xmark & \cmark & \xmark & \xmark & \cmark & \xmark & \cmark & \xmark & \xmark & \xmark \\
            \bottomrule
        \end{tabular}
        }
    \end{center}
\end{sidewaystable*}

>>>>

\begin{figure}[!t]
    \begin{flushleft}
        \textsc{\small \hspace{0.16\textwidth} self-supervised \hspace{0.22\textwidth} latent variable}
    \end{flushleft}
    \centering
    \includegraphics[width=0.90\textwidth]{paper_brief/SSL_LVM.pdf}
    \caption[ schematic overview of the self-supervised and probabilistic latent variable models covered in this survey.]{A schematic overview of the two groups of models covered in this survey. \textit{Left}: A model trained with self-supervised learning. We take these models to consist of two functions $f(\cdot)$ and $g(\cdot)$ (\cref{ssec:notation}). After pre-training, $f(\cdot)$ is fine-tuned or used for extracting features $\mathbf{c}$. $g(\cdot)$ is an auxiliary function used to accommodate the self-supervised pre-training task. \textit{Right}: A probabilistic latent variable model. In contrast to the self-supervised model, the functions $f(\cdot)$ and $g(\cdot)$ learn the parameters of distributions $q$ and $p$. The latent variable $\mathbf{z}$ is commonly used for representation learning.}
    \label{fig:ssl_lvm}
\end{figure}

@@

\begin{sidewaystable*}[t]
    \caption[Classification of selected self-supervised and probabilistic latent variable models.]{Selected models classified according to the binary attributes identified throughout the text. The models are sorted according to first publication date on arXiv which might differ from the citation year. \textbf{\textsc{msk}}: masking, \textbf{\textsc{prd}}: prediction, \textbf{\textsc{con}}: contrastive, \textbf{\textsc{rec}}: reconstruction, \textbf{\textsc{qtz}}: quantization, \textbf{\textsc{gen}}: generative, \textbf{\textsc{frz}}: frozen, \textbf{\textsc{ftn}}: fine-tuned, \textbf{\textsc{loc}}: local, \textbf{\textsc{glo}}: global.}
    \label{tab:model-taxonomy}
    \begin{center}
        \renewcommand{\arraystretch}{1.1}
        \resizebox{0.925\textwidth}{!}{%
        \begin{tabular}{ l l | c c c c c c | c c c | c c } 
            \toprule

@@

\begin{table}[t!]
\caption[A comprehensive overview of observation, prior and inference models for VAE type latent variable models with a single latent variable.]{A comprehensive overview of observation, prior and inference models for VAE type latent variable models with a single latent variable. The observation, prior and inference models may all belong to one or more of the categories listed under them as detailed in \cref{sec:plvms}. The types listed here serve as primitives from which more complex structures can be constructed including models with hierarchies of multiple latent variables.}
\label{tab:lvm-model-primitives}
\begin{center}
    % \renewcommand{\arraystretch}{1.1}
    % \resizebox{0.8\columnwidth}{!}{%
    \begin{tabular}{ l l l } 
        \toprule
        \multicolumn{2}{l}{\textbf{\textsc{Type}}} & \textbf{\textsc{Form}} \\
        \midrule
        \multicolumn{3}{c}{\textsc{Observation model}} \\
        \midrule
        \textbf{\textsc{arx}} & Autoregressive on $\mathbf{x}_t$      & $p(\mathbf{x}_t|\mathbf{x}_{1:t-1})$ \\
        \textbf{\textsc{loc}} & Local latent variable                 & $p(\mathbf{x}_{t}|\mathbf{z}_{1:t})$ \\
        \textbf{\textsc{glb}} & Global latent variable                & $p(\mathbf{x}_{t}|\mathbf{z})$ \\
        \midrule
        \multicolumn{3}{c}{\textsc{Prior}} \\
        \midrule
        \textbf{\textsc{arx}} & Autoregressive on $\mathbf{x}_t$      & $p(\mathbf{z}_t|\mathbf{x}_{1:t-1})$ \\
        \textbf{\textsc{arz}} & Autoregressive on $\mathbf{z}_t$      & $p(\mathbf{z}_t|\mathbf{z}_{1:t-1})$ \\
        \textbf{\textsc{ind}} & Locally independent $\mathbf{z}_t$                 & $p(\mathbf{z}_t)$ \\
        \textbf{\textsc{glb}} & Global latent variable                & $p(\mathbf{z})$ \\
        \midrule
        \multicolumn{3}{c}{\textsc{Inference model}} \\
        \midrule
        \textbf{\textsc{arz}} & Autoregressive on $\mathbf{z}_t$      & $q(\mathbf{z}_t|\mathbf{z}_{1:t-1})$ \\
        \textbf{\textsc{flt}} & Filtering                             & $q(\mathbf{z}_t|\mathbf{x}_{1:t})$ \\
        \textbf{\textsc{lsm}} & Local smoothing                       & $q(\mathbf{z}_t|\mathbf{x}_{t-r:t+r})$ \\
        \textbf{\textsc{gsm}} & Global smoothing                      & $q(\mathbf{z}_t|\mathbf{x}_{1:T})$ \\
        \textbf{\textsc{glb}} & Global latent variable                & $q(\mathbf{z}|\mathbf{x}_{1:T})$ \\
        \bottomrule
    \end{tabular}
    % }
    \end{center}
\end{table}

\begin{sidewaystable*}[t]
    \caption[Classification of selected latent variable models.]{Selected latent variable models classified according the attributes defined throughout \cref{sec:plvms}. See \cref{tab:lvm-model-primitives} for the probability distributions that correspond to each of the attribute short-hands. \textbf{\textsc{hie}} indicates a hierarchical representation.}
    \label{tab:lvm-taxonomy}
    \begin{center}
        \renewcommand{\arraystretch}{1.1}
        \resizebox{0.99\textwidth}{!}{% <------ Don't forget this %
        \begin{tabular}{ l l | c c c | c c c c | c c c c c | c } 
            \toprule
            \multicolumn{2}{c}{} & 
            \multicolumn{3}{c}{\footnotesize\textsc{Observation}} & 
            \multicolumn{4}{c}{\footnotesize\textsc{Prior}} & 
            \multicolumn{5}{c}{\footnotesize\textsc{Inference}} \\
            \textbf{\textsc{model}} & 
            \textbf{\textsc{pub. date}} &
            \textbf{\textsc{arx}} & 
            \textbf{\textsc{loc}} & 
            \textbf{\textsc{glb}} &  
            \textbf{\textsc{arx}} & 
            \textbf{\textsc{arz}} & 
            \textbf{\textsc{ind}} & 
            \textbf{\textsc{glb}} &  
            \textbf{\textsc{arz}} & 
            \textbf{\textsc{flt}} & 
            \textbf{\textsc{lsm}} & 
            \textbf{\textsc{gsm}} & 
            \textbf{\textsc{glb}} &
            \textbf{\textsc{hie}} \\
            \midrule
            %                                                              OBSERVATION       |              PRIOR                |                  INFERENCE       
            %                                                         ARX      LOC      GLB      ARX      ARZ     IND      GLB      ARZ      FLT      LSM      GSM      GLB
            \textbf{VRNN} \footnotesize\parencite{chung_recurrent_2015}          & 2015 Jun. & \cmark & \cmark & \xmark & \cmark & \cmark & \xmark & \xmark & \cmark & \cmark & \xmark & \xmark & \xmark & \xmark \\
            \textbf{SRNN} \footnotesize\parencite{fraccaro_sequential_2016}      & 2016 May  & \cmark & \cmark & \xmark & \cmark & \cmark & \xmark & \xmark & \cmark & \xmark & \xmark & \cmark & \xmark & \xmark \\
            \textbf{HMM-VAE} \footnotesize\parencite{ebbers_hidden_2017}         & 2017 Mar. & \xmark & \cmark & \xmark & \xmark & \cmark & \xmark & \xmark & \cmark & \cmark & \xmark & \xmark & \xmark & \cmark \\
            \textbf{ConvVAE} \footnotesize\parencite{hsu_learning_2017}          & 2017 Apr. & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark & \cmark & \cmark & \xmark \\
            \textbf{FHVAE} \footnotesize\parencite{hsu_unsupervised_2017}        & 2017 Sep. & \xmark & \cmark & \cmark & \xmark & \xmark & \cmark & \cmark & \xmark & \xmark & \xmark & \cmark & \cmark & \cmark \\
            \textbf{VQ-VAE} (van den Oord et al. 2018)            & 2017 Nov. & \cmark & \cmark & \xmark & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark \\
            \textbf{BHMM-VAE} \footnotesize\parencite{glarner_full_2018}         & 2018 Mar. & \xmark & \cmark & \xmark & \xmark & \cmark & \xmark & \xmark & \cmark & \cmark & \xmark & \xmark & \xmark & \xmark \\
            \textbf{STCN} \footnotesize\parencite{aksan_stcn_2019}               & 2019 Feb. & \xmark & \cmark & \xmark & \cmark & \xmark & \xmark & \xmark & \xmark & \cmark & \xmark & \xmark & \xmark & \cmark \\
            \textbf{FDMM} \footnotesize\parencite{khurana_factorial_2019}        & 2019 Oct. & \xmark & \cmark & \cmark & \xmark & \cmark & \xmark & \cmark & \cmark & \cmark & \xmark & \xmark & \cmark & \cmark \\
            \textbf{ConvDMM} \footnotesize\parencite{khurana_convolutional_2020} & 2020 Jun. & \xmark & \cmark & \xmark & \xmark & \cmark & \xmark & \xmark & \cmark & \xmark & \cmark & \xmark & \xmark & \xmark \\
            \bottomrule
        \end{tabular}
        }
    \end{center}
\end{sidewaystable*}

### 2023-10-03 appendices/supplementary_retrospective.tex
Work on abstract and discussion

\begin{table}[h]
    \centering
    \caption{Overall performance on MH-1813 test data for the model that also takes patient age and sex as direct inputs. We also list the original performance of call-takers and the model (w/o sex and age) from the main manuscript for ease of comparison [mean (95\% CI)].}
    \label{tab_retrospective:tableA4}
    \resizebox*{0.98\textwidth}{!}{%
    \begin{tabular}{l|ccccc}
        \toprule
        & F1-score [\%] $\uparrow$ & Sensitivity [\%] $\uparrow$ & PPV [\%] $\uparrow$ & \makecell[c]{FOR [\%] $\downarrow$ \\ (1 - NPV)} & \makecell[c]{FPR [\%] $\downarrow$ \\ (1 - specificity)} \\
        \midrule
        & \multicolumn{5}{c}{\textit{Overall}} \\
        \midrule

@@

\begin{table}[h]
    \centering
    \caption{Overall performance on MH-1813 test data for the model that also takes patient age and sex as direct inputs. We also list the original performance of call-takers and the model (w/o sex and age) from the main manuscript for ease of comparison [mean (95\% CI)].}
    \label{tab_retrospective:tableA8}
    \resizebox*{0.98\textwidth}{!}{%
    \begin{tabular}{l|ccccc}
        \toprule
        & F1-score [\%] $\uparrow$ & Sensitivity [\%] $\uparrow$ & PPV [\%] $\uparrow$ & \makecell[c]{FOR [\%] $\downarrow$ \\ (1 - NPV)} & \makecell[c]{FPR [\%] $\downarrow$ \\ (1 - specificity)} \\
        \midrule
        & \multicolumn{5}{c}{\textit{Overall}} \\
        \midrule

>>>>

\begin{table}[h]
    \centering
    \caption[Overall performance on MH-1813 test data for the model that also takes patient age and sex as direct inputs.]{Overall performance on MH-1813 test data for the model that also takes patient age and sex as direct inputs. We also list the original performance of call-takers and the model (w/o sex and age) from the main manuscript for ease of comparison [mean (95\% CI)].}
    \label{tab_retrospective:tableA4}
    \resizebox*{0.98\textwidth}{!}{%
    \begin{tabular}{l|ccccc}
        \toprule
        & F1-score [\%] $\uparrow$ & Sensitivity [\%] $\uparrow$ & PPV [\%] $\uparrow$ & \makecell[c]{FOR [\%] $\downarrow$ \\ (1 - NPV)} & \makecell[c]{FPR [\%] $\downarrow$ \\ (1 - specificity)} \\
        \midrule
        & \multicolumn{5}{c}{\textit{Overall}} \\
        \midrule

@@

\begin{table}[h]
    \centering
    \caption[Overall performance on MH-1813 test data for a fine-tuned BERT model.]{Overall performance on MH-1813 test data for a fine-tuned BERT model. We also list the original performance of call-takers and the ensemble model from the main manuscript for ease of comparison [mean (95\% CI)].}
    \label{tab_retrospective:tableA8}
    \resizebox*{0.98\textwidth}{!}{%
    \begin{tabular}{l|ccccc}
        \toprule
        & F1-score [\%] $\uparrow$ & Sensitivity [\%] $\uparrow$ & PPV [\%] $\uparrow$ & \makecell[c]{FOR [\%] $\downarrow$ \\ (1 - NPV)} & \makecell[c]{FPR [\%] $\downarrow$ \\ (1 - specificity)} \\
        \midrule
        & \multicolumn{5}{c}{\textit{Overall}} \\
        \midrule

### 2023-10-03 chapters/discussion.tex
Work on abstract and discussion

\section{\Cref{chp:paper-retrospective} revisited: Uncertainty}
The work in \textcite{wenstrup_retrospective_2023} focuses on the predictive performance of the ensemble model and an analysis of feature importance, but does not explicitly consider uncertainty estimation. 
As we discussed in \cref{subsec:model-calibration}, such a model can be calibrated to predict probabilities that are aligned with the empirical probability of the model being correct on some validation set.

@@

To calibrate the ensemble model, we can use methods such as Platt-scaling \parencite{platt_probabilistic_1999} or isotonic regression \parencite{zadrozny_transforming_2002}. 
In both cases, we fit a simple regression model (logistic or isotonic) to the predicted probabilities and the target labels on some validation set. 
In \cref{fig_discussion:retrospective-paper-calibration-curve-sigmoid-isotonic} we have done so for the ensemble model using our validation set for fitting and visualizing the results on the test set. On the left, we plot the resulting calibration curves and on the right we show the logistic and isotonic fits. We see that both methods result in quite good calibrations\footnote{Brier scores: Uncalibrated = $0.003500$, logistic = $0.001807$, isotonic = $0.001774$. Brier skill score compared to uncalibrated (relative improvement): Logistic = $0.4830$, isotonic = $0.4924$} and that the predicted probabilities are shifted towards smaller values.

However, while correct calibration provides some interpretability to the predictions, the resulting probabilities are still functions of the model's performance. For example, with the logistic calibration, we can note that the predicted probabilities have been shifted so far towards smaller values that the best the model can do, is a predicted probability of about 50\%. This means strokes can be predicted at best with 50\% probability of being correct. 
If this model were to be deployed in a randomized controlled trial, the calibrated probabilities might be useful to incorporate in the design of the user interface such that a user can discern between confident and uncertain model predictions. Nonetheless, it is easy to imagine how this generally low confidence might lead the user to ignore the model.

>>>>

\section{\Cref{chp:paper-retrospective} revisited: Calibration}
The work in \textcite{wenstrup_retrospective_2023} focuses on the predictive performance of the ensemble model and an analysis of feature importance, but does not explicitly consider uncertainty estimation. 
As we discussed in \cref{subsec:model-calibration}, such a model can be calibrated to predict probabilities that are aligned with the empirical probability of the model being correct on some validation set.

@@

To calibrate the ensemble model, we can use methods such as Platt-scaling \parencite{platt_probabilistic_1999} or isotonic regression \parencite{zadrozny_transforming_2002}. 
In both cases, we fit a simple regression model (logistic or isotonic) to the predicted probabilities and the target labels on some validation set. 
In \cref{fig_discussion:retrospective-paper-calibration-curve-sigmoid-isotonic} we have done so for the ensemble model using our validation set for fitting and visualizing the results on the test set. On the left, we plot the resulting calibration curves and on the right we show the logistic and isotonic fits. We see that both methods result in quite good calibrations\footnote{Test set Brier scores: Uncalibrated = $0.003500$, logistic = $0.001807$, isotonic = $0.001774$. Brier skill score compared to uncalibrated (relative improvement): Logistic = $0.4830$, isotonic = $0.4924$.} and that the predicted probabilities are shifted towards smaller values.

While correct calibration provides some interpretability to the predictions, the actual values of the probabilities are still tied of the model's performance. For example, with the logistic calibration, we can note that the predicted probabilities have been shifted so far towards smaller values that the highest possible predicted probability is about 50\%. This means strokes can be predicted at best with a 50\% chance of being correct. 
If this model were to be deployed in a randomized controlled trial, the calibrated probabilities might be incorporated in the design of the user interface such that a user can discern between confident and uncertain model predictions. However, it is easy to imagine how this generally low confidence might lead the user to ignore the model. This highlights a problem with uncertainties

### 2023-10-03 chapters/introduction.tex
Work on abstract and discussion

\begin{figure}[t]
    \centering
    % \includegraphics[width=0.90\textwidth]{plimpton_322.png}
    \includegraphics[height=0.4\textheight]{plimpton_322.png}
    \caption{Technology is difficult. The scribe of the Plimpton 322 clay tablet ($\sim$1800 BCE) made several errors when listing Pythagorean triplets, presumably struggling to grapple with Babylonian mathematics. \parencite[photo credit][]{neugebauer_mathematical_1945}}
    \label{fig:plimpton_332}
\end{figure}

@@

\begin{figure}[t]
    \centering
    % \includegraphics[width=0.95\textwidth]{eniac_programmers.jpeg}
    \includegraphics[height=0.4\textheight]{eniac_programmers.jpeg}
    \caption{Ruth Lichterman (left) and Marlyn Wescoff (middle) were two of the several female programmers of the ENIAC. \parencite[photo credit][]{usarmyresearchlaboratoryarltechnicallibrary_female_1940}} %Photo: \copyright Corbis/ Getty Images.}
    \label{fig:eniac_programmers}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.90\textwidth]{uber_nhsa_accident.png}
    \caption{A pedestrian was killed by an Uber self-driving car in Tempe, Arizona in 2018. The car's sensors detected the pedestrian $5.6$ seconds before the crash, but the self-driving system failed to recognize its own uncertainty in multiple object misclassifications and so did not correctly predict her path or reduce the SUV's speed \parencite[photo credit][]{nationaltransportationsafetyboardnhsa_collision_2019}.}
    % \caption{Aerial view of crash location showing path of pedestrian as she attempted to cross N. Mill Avenue and movement and speed of SUV at three points before impact. Pedestrian's path shows her position from initial detection ($5.6$ seconds before impact) until impact; SUV's position is shown at corresponding times beginning $4.2$ seconds before impact \parencite{nationaltransportationsafetyboardnhsa_collision_2019}.}
    \label{fig:uber_nhsa_accident}
\end{figure}

>>>>

\begin{figure}[t]
    \centering
    % \includegraphics[width=0.90\textwidth]{plimpton_322.png}
    \includegraphics[height=0.4\textheight]{plimpton_322.png}
    \caption[Technology is difficult. The scribe of the Plimpton 322 clay tablet ($\sim$1800 BCE) made several errors when listing Pythagorean triplets.]{Technology is difficult. The scribe of the Plimpton 322 clay tablet ($\sim$1800 BCE) made several errors when listing Pythagorean triplets, presumably struggling to grapple with Babylonian mathematics. \parencite[photo credit][]{neugebauer_mathematical_1945}}
    \label{fig:plimpton_332}
\end{figure}

@@

\begin{figure}[t]
    \centering
    % \includegraphics[width=0.95\textwidth]{eniac_programmers.jpeg}
    \includegraphics[height=0.4\textheight]{eniac_programmers.jpeg}
    \caption[Ruth Lichterman (left) and Marlyn Wescoff (middle) were two of the several female programmers of the ENIAC.]{Ruth Lichterman (left) and Marlyn Wescoff (middle) were two of the several female programmers of the ENIAC. \parencite[photo credit][]{usarmyresearchlaboratoryarltechnicallibrary_female_1940}}
    \label{fig:eniac_programmers}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.90\textwidth]{uber_nhsa_accident.png}
    \caption[A pedestrian was killed by an Uber self-driving car in Tempe, Arizona in 2018.]{A pedestrian was killed by an Uber self-driving car in Tempe, Arizona in 2018. The car's sensors detected the pedestrian $5.6$ seconds before the crash, but the self-driving system failed to recognize its own uncertainty in multiple object misclassifications and so did not correctly predict her path or reduce the SUV's speed \parencite[photo credit][]{nationaltransportationsafetyboardnhsa_collision_2019}.}
    % \caption{Aerial view of crash location showing path of pedestrian as she attempted to cross N. Mill Avenue and movement and speed of SUV at three points before impact. Pedestrian's path shows her position from initial detection ($5.6$ seconds before impact) until impact; SUV's position is shown at corresponding times beginning $4.2$ seconds before impact \parencite{nationaltransportationsafetyboardnhsa_collision_2019}.}
    \label{fig:uber_nhsa_accident}
\end{figure}
